Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-12 arxiv-version/main.tex
Work on the introduction

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}

@@

\begin{abstract}
TODO
\end{abstract}

\section{Introduction}

We study the online multiclass classification problem with bandit feedback. The
problem was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
corresponding problem with full information feedback is solved by the classical
\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
natural and potential applications include online advertising and online content
optimization.

In this paper, we focus on the special case when the data is \emph{linearly
separable with a margin}. In the full-information feedback setting, it is well
know that if the data set lies in the ball of radius $R$ centered at the origin
and is linearly separable with a margin $\gamma$ then the \textsc{Multiclass
Perceptron} algorithm makes at most $(R/\gamma)^2$ mistakes. This result very
satisfactory since the upper bound on the number of mistakes is
information-theoretically optimal and at the same time the \textsc{Multiclass
Perceptron} algorithm has low time and memory complexity.

The bandit feedback setting, however, is much more challenging. We propose three
algorithms with various time-complexity-versus-mistake-bound trade-offs. Two of
these algorithms map the data into a high-dimensional space induced by a kernel.
In this space the data become so called \emph{strongly separable} making the
learning essentially trivial. The two algorithms differ by the choice of the
kernel. The crux of the problem is th analysis of approximation properties of
these kernels and has been studied previously by \cite{???} in the context of
learning intersection of halfspaces. The third algorithm is based on the obvious
idea that two points that are close enough must have the same label. Here, close
enough means that they cannot be separated from each other by a linear separator
with a margin.

All three algorithms run in time that is polynomial in the dimension of the
feature vectors, the number of classes and the number of rounds. At the same
time, all three algorithms make number of mistakes that does \emph{not} depend
on the number of rounds only on the margin, number of classes, dimension of the
feature vectors, and the radius of the ball in which the data lie.

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly-labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for a particular one class. First,
we show the offline problem of finding any linear separator consistent with
given set of strongly- and weakly-labeled examples is NP-hard. Second, we show
that any algorithm that ignores weakly labeled examples must make at least
$\Omega(???)$ mistakes.

\bibliographystyle{plainnat}
\bibliography{biblio}
